%20171114-155627
\documentclass{article} 
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{paralist}
\usepackage{algorithm, algorithmic}
\usepackage{mathtools}

\input{macros}
\begin{document}

\section{Announcement Types}

In what follows, we consider that agents
only make particular kinds of announcements.
We then consider protocols built up using such
announcements and perform an analysis of such
protocols. An agent $p$ may announce,
\begin{compactenum}
\item $ann(X)$ $\quad \coloneq \quad$ that his cards are a subset of $H_p \cup X$.
\item $\top$ $\quad \coloneq \quad$ an announcement equivalent to pass.
\end{compactenum}

\section{Protocols}

To construct a protocol, consider 
strategy \ref{s1} described below.

\begin{algorithm}
\floatname{algorithm}{Strategy}
\caption{S1($p$)}
\label{s1}
\begin{algorithmic}[1]
\STATE $ann(X_{p}^1)$ where $|X_p^1| = 2$ and $X_p^1 \cap H_p = \emptyset$ 
\STATE announce $ann(X_p^2)$ where $X_p^2 \subseteq X_P^1$
\end{algorithmic}
\end{algorithm}

A complete protocol $\pi_1$ is obtained when each agent
runs strategy \ref{s1} independently of each other. That
is, when making an announcement each agent is free to
choose $X_p^i$ as he wills (independent of history). 
Some points to note

\begin{compactenum}[\label=a)]
\item The announcement sequence is actually safe when others pass.
\item Nevertheless the final protocol might leak information to $\cal E$.
\item So, the question would be how bad is it? 
\item Does the protocol converge?
\item How much information is transferred among the agents?
\end{compactenum}

\section{Analysis}
In what follows, we tabulate the results for
sample executions for $\langle 4 | 4 | 4 \rangle$.
The setup as well as the executions used are detailed 
in Section \ref{appdx:exec}.

\subsection{Safety}
Safety depends on what Eaves knows (first order) after
any run. We tabulate some parameters relevant for
evaluating a run below. In particular, pos refers
to positive knowledge while neg refers to negative
knowledge and nD refers to number of deals.

\newpage
\appendix
\input{appendix}
\end{document}
%20171114-155627
